### 2021-03-19 doc/manuscript/Dow_manuscript_Nature.Rmd
compiled draft DOY timing figure with stem growth + foliage
#50

DOYtiming_caption <- "Figure 3 | Day of year where growth milestones were achieved at (a) the Smithsonian Conservation Biology Institute and (b) Harvard Forest. Each line represents a single year of ring-porous (dotted line) or diffuse-porous (solid line) trees at each site. Mean temperature was calculated for each wood-type/site combination over the respective critical $T_{max}$ window, then turned into a ratio and assigned a color on a gradient where the coldest year in the sample is blue and the warmest is red. (WE WILL ADD LEAF PHENOLOGY HERE)"

@@

As global atmospheric CO~2~ concentrations increase and Earth's temperatures increase, the responses and feedbacks of forests will play an important yet uncertain role in influencing atmospheric CO~2~ and climate change[@bonan_forests_2008; @friedlingstein_climate_2006]. 
Temperate deciduous forests, including those in eastern North America, *(have been net carbon sinks over the past several decades)*... 
*[Discuss this sink, mechanisms, uncertainties, ending with the point that one meaningful uncertainty is how the C sink will respond to warming springs]*

@@

```{r DOYtiming, out.width="100%", echo=FALSE, fig.align="center", fig.cap= DOYtiming_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/DOYtiming_allyears.png")
```

>>>>

DOYtiming_caption <- "Figure 3 | Leaf (a,b) and stem growth (c,d) phenology at the Smithsonian Conservation Biology Institute (a,c) and Harvard Forest (b,d) from 1998 to 2020 (when available). **DRAFT FIGURE-- REAL DATA BUT NEEDS FORMATTING.** Panels (a-b) show leaf phenology... Panels (c-d) show the dates at which stem growth milestones were acheived, on average, for sampled populations of ring-porous and diffuse-porous trees at each site. Mean temperature was calculated for each wood-type/site combination over the respective critical $T_{max}$ window, then turned into a ratio and assigned a color on a gradient where the coldest year in the sample is blue and the warmest is red."

@@

As global atmospheric CO~2~ concentrations increase and Earth's temperatures increase, the responses and feedbacks of forests will play an important yet uncertain role in influencing atmospheric CO~2~ and climate change[@arora_carbon_2020; @friedlingstein_global_2020]. 
Temperate deciduous forests, including those in eastern North America, *(have been net carbon sinks over the past several decades)*... 
*[Discuss this sink, mechanisms, uncertainties, ending with the point that one meaningful uncertainty is how the C sink will respond to warming springs]*

@@

```{r DOYtiming, out.width="100%", echo=FALSE, fig.align="center", fig.cap= DOYtiming_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/DOYtiming_stemgrowth+foliage.png")
```
